\documentclass{article}
\usepackage{times}
\usepackage{a4wide}
\usepackage{latexsym}
\usepackage{mathrsfs}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{ifthen}
\usepackage{stmaryrd}
\usepackage{algorithm}
%\usepackage{algorithmic}
\usepackage{algpseudocode}
\usepackage{graphics}
\usepackage{epsfig}
%\usepackage{ramacros}

\addtolength{\textwidth}{20mm}
\addtolength{\oddsidemargin}{-10mm}
\addtolength{\textheight}{18mm}
\addtolength{\topmargin}{-9mm}

\newcounter{exercise}
\setcounter{exercise}{0}
\newcommand{\exercise}{
        \addtocounter{exercise}{1}
        \vspace{0.2in}
        \noindent
        {\bf \theexercise .}
        }

\newcommand{\REMARK}[1]{}


\newcommand{\NEWPART}{\vspace{.1in}
              \noindent}

\newcommand{\<}{
    \langle}

\renewcommand{\>}{
    \rangle}

\newcommand{\ceil}[1]{\left\lceil #1 \right\rceil}

\pagestyle{plain} \pagenumbering{arabic}

\title{{\bf Assignment 5} \\ {\large ID: 120037910002 } {\large Name: Xingguo Jia } {\large Email: jiaxg1998@sjtu.edu.cn}}

\author{}
\date{}

\begin{document}
\maketitle

%{\large \noindent
%\begin{tabular}{lcl}
%{Jan 17 2007}.
%\end{tabular}
%}

{\large
Note: in this assignment, we use $m$ to denote the object function value achieved by the \textbf{approximation algorithm} and $m^*$ to denote $OPT$.
\newline

\begin{exercise}
Use layering to get a factor $f$ approximation algorithm for set cover,
where $f$ is the frequency of the most frequent element. Provide a tight example
for this algorithm.

\end{exercise}

\textbf{Algorithm:}
Suppose $I={S_1,S_2,\ldots,S_n}$ are the subsets of $E$, $C\leftarrow \phi,i\leftarrow 0$,$E_0\leftarrow E$
\begin{enumerate}
	\item Move all empty sets from $I_i$ to $D_i$
	\item Let $c=min\{w(S)/|S|\}$ for all $S\in I_i$
	\item $t_i(S)=c*|S|,w(S)\leftarrow w(S)-t_i(S)$ for all $S\in I_i$
	\item $W_i\leftarrow \{S\in I_i \mid w(S)=0\},C\leftarrow C\cup W_i$
	\item $I_{i+1}\leftarrow I_{i}-(D_i\cup W_i), E_{i+1}\leftarrow E_{i}-(D_i\cup W_i)$
	\item $i\leftarrow i+1$, repeat step 2
\end{enumerate}
\begin{itemize}
	\item We prove that if $w(S)/|S|=c$ for all $S\in I_i$, then $w(I)\leq f*OPT$. We have
	$$
	|E|\leq \sum_{S_i\in U}{|S_i|} \Rightarrow c|E|\leq c\sum_{S_i\in U}{|S_i|}=OPT
	$$
	\item and
	$$
	\sum_{S_i\in I}{|S_i|}\leq f*|E|\Rightarrow c*\sum_{S_i\in I}{|S_i|}\leq c*f*|E|\leq f*OPT
	$$
	\item Then we prove this is an $f$ approximation algorithm for set cover. We have
	$$
	w(C)=\sum_{i=0}^{k-1}{t_i(C\cap I_i)}\leq f*\sum_{i=0}^{k-1}{t_i(U\cap I_i)}\leq f*w(U)=f*OPT
	$$
	\item Tight example:
	$$
	E=\{e_1,e_2,\ldots,e_n\},i=\{S_1,S_2,\ldots,S_f\}
	$$
	\item where
	$$
	S_i=E,w(S_i)=1,i=1,\ldots,f
	$$
	\item The algorithm would choose all $S_i\in I$, which has weight $m=f$. Optimal solution is $m^*=1$, Thus
	$$
	\frac{m}{m^*}=f
	$$
\end{itemize}


\newpage

\begin{exercise}
	Let $G = (V, E)$ be an undirected graph with nonnegative edge costs. $S$, the senders and $R$, the receivers, are disjoint subsets of $V$. The problem is to find a minimum cost subgraph of $G$ such that for every receiver $r$ in $R$, there is at least one sender $s$ in $S$ such that there is a path connecting $r$ to $s$ in the subgraph. Give a factor $2$ approximation algorithm that runs in polynomial time.
\end{exercise}

\textbf{Solution:}
\begin{itemize}
	\item Add a vertex $v$ and edges $(v,s)$ for all $s\in S$ with cost $0$, and we get graph $G'$.
	\item Run MST-based algorithm on $G'$ where $\{v\}\cup R$ is the required set of vertices, and the result is tree $T'$. We remove vertex $v$ from $T'$ and get $T$. For any $r\in R$, since there is a path connecting $r$ and $v$ in $T$ and this path must go through some $s\in S$, there is a path connecting $r$ and some $s\in S$.
	\item Thus, $T$ is a subgraph of $G$ such that for every receiver $r$ in $R$, there is at least one sender $s$ in $S$ such that there is a path connecting $r$ to $s$ in the $T$, which is a factor $2$ approximation.
\end{itemize}
\newpage




\begin{exercise}
	\textbf{(Bin Packing)} Consider a more restricted algorithm than First-Fit, called Next-Fit, which tries to pack the next item only in the most recently started bin. If it does not fit, it is packed in a new bin. Show that this algorithm also achieves factor $2$. Give a factor $2$ tight example.
\end{exercise}

\textbf{Solution:}
\begin{itemize}
	\item Suppose we use $N$ bins by the Next-Fit algorithm, and each bin has $0\leq A_i\leq 1\ (i=1,\ldots ,N)$ amount of item.
	\item Consider two adjacent bins $j$ and $j+1\ (1\leq j\leq N-1)$, we have
	$$
	A_j + A_{j+1}>1
	$$
	\item Thus we have
	$$
	2*OPT\geq 2*\sum{A_i}=A_1+\sum\limits_{j=1}^{N-1}{(A_j + A_{j+1})}+A_N>\sum\limits_{j=1}^{N-1}{(A_j + A_{j+1})}>N-1
	$$
	\item Which implies $2*OPT\geq N$.
	\item Tight Example: let $0<\epsilon\leq \frac{1}{n}$, we have $2*n$ items
	$$
	A_{2i-1}=2\epsilon,A_{2i}=1-\epsilon,i=1,\ldots,n
	$$
	\item Run the Next-Fit algorithm, we need $m=2n$ bins, but actually, we put $A_{2i-1},i=1,\ldots,n$ all in one bin, and each $A_{2i}$ in one bin, we get $m^*=n+1$ bins. Let $n\rightarrow +\infty$, we have 
	$$
	\frac{m}{m^*}=2
	$$.
\end{itemize}
\newpage



\begin{exercise}
	\textbf{(Hamilton cycle)} Given an undirected complete graph, each edge is assigned with a nonnegative cost by the function $c$ (eg. the cost for edge $(u,v)$ is $c(u,v)$). Find a Hamilton cycle with the largest cost by the greedy approach, and prove the guarantee factor is $2$.
\end{exercise}

\textbf{Solution:}

\begin{algorithm}[htb]
\caption{Greedy-Algorithm for MAX Hamilton cycle}
\begin{algorithmic}[1]
\State Choose a random vertex $v\in V$, let
\State $C\leftarrow \{v\}$
\While{$|C|<|V|$}
	\State $C\leftarrow C\cup {v_m}$, s.t. $c(v,v_m)\geq c(v,v_i)$, $\forall v_i\in V$
	\State $v\leftarrow v_m$
\EndWhile
\State
\Return $C$
\end{algorithmic}
\end{algorithm}

\begin{itemize}
	\item We prove Algorithm 1 has a guarantee factor of $2$. Let 
	$$
	C=v_{1}v_{2}\ldots v_{|V|}
	$$
	\item and the optimal solution is 
	$$
	O=v_{t_1}v_{t_2}\ldots v_{t_{|V|}}
	$$
	\item For $1\leq i\leq |V|-1$, we have
	$$
	c(v_{t_i},v_{t_{i+1}})\leq max\{c(v_{t_i},v_{t_i+1}),c(v_{t_{i+1}},v_{t_{i+1}+1})\}
	\leq c(v_{t_i},v_{t_i+1})+c(v_{t_{i+1}},v_{t_{i+1}+1})
	$$
	\item Thus
	$$
	m=\sum{c(v_i,v_{i+1})}=\sum{c(v_{t_i},v_{t_i+1})} = 
	$$
	$$
	\frac{1}{2}*\sum{(c(v_{t_i},v_{t_i+1}) + c(v_{t_{i+1}},v_{t_{i+1}+1}))}\geq \frac{1}{2}*\sum{c(v_{t_i},v_{t_{i+1}})}=\frac{1}{2}*m^*=\frac{1}{2}*OPT
	$$
\end{itemize}
\newpage




\begin{exercise}
	Given a directed graph $G=(V,E)$, we need to pick a maximum cardinality set of edges from $E$ so that the resulting subgraph is acyclic. Find a factor $\frac{1}{2}$ approximate algorithm for this problem.
\end{exercise}

\textbf{Solution:}
\begin{itemize}
	\item Assign a unique integer $f(v_i)$ for each vertex $v_i\in V$. For each edge $(v_i, v_j)\in E$, it is in either of the two sets:
	$$
	A=\{(v_i, v_j)\mid(v_i, v_j)\in E, f(v_i)>f(v_j)\}, B=\{(v_i, v_j)\mid(v_i, v_j)\in E, f(v_i)<f(v_j)\}
	$$
	\item There is no cycle in $A$ or $B$. WLOG, $|A|\geq |B|$. Let $A$ be the result, then we have
	$$
	m=|A|=\frac{|A|}{2}+\frac{|A|}{2}\geq\frac{|A|}{2}+\frac{|B|}{2}=\frac{|E|}{2}=\frac{m^*}{2}
	$$
\end{itemize}
\newpage





\begin{exercise}
	\textbf{(Knapsack)} Given a set $S = \{a_1, ... , a_n\}$ of objects, with specified non-negative weights and profits, $w_i,p_i$ respectively, and a "knapsack capacity" $B (w_i \le B)$, find a subset of objects whose total weight is bounded by $B$ and total profit is maximized.
	
	1. Consider two types of greedy algorithms for the knapsack problem. Sort the objects by decreasing \textbf{ratio of profit to weight} or only by \textbf{profit}, and then greedily pick objects in this order. Show that these two algorithms can be made to perform arbitrarily badly.
	
	2. Combining these two greedy algorithm, pick the more profitable solution in these two algorithms' results. Show that this algorithm achieves an approximation factor of $2$.
\end{exercise}

\textbf{Solution:}
\begin{itemize}
	\item Let $\epsilon$ be an arbitrarily small number, and $n$ be an arbitrarily large number.
	\item \textbf{(ratio of profit to weight)} 
	$$
	(w_1,p_1)=(2\epsilon,3\epsilon),(w_2,p_2)=(B-\epsilon,B-\epsilon)
	$$
	\item The algorithm would choose the first item but cannot choose the second item, which has an approximation factor of 
	$$
	\frac{m}{m^*}=\frac{3\epsilon}{B-\epsilon}\rightarrow 0
	$$
	\item \textbf{(profit)} 
	$$
	(w_1,p_1)=(\epsilon,B-\epsilon),(w_2,p_2)=(\epsilon,B-\epsilon),\ldots,(w_n,p_n)=(\epsilon,B-\epsilon),(w_{n+1},p_{n+1})=(B,B)
	$$
	\item Then the algorithm would choose the last item, which has an approximation factor of
	$$
	\frac{m}{m^*}=\frac{B}{n*(B-\epsilon)}= \frac{1}{n*(1-\frac{\epsilon}{B})}\rightarrow 0
	$$
	\item By combining the two algorithms, we mean running the both two algorithms on the same data, and get the more profitable result. Sort the items by \textbf{ratio of profit to weight} and we have $k$ where
	$$
	\sum_{i=1}^{k}{w_i}\leq B, \sum_{i=1}^{k+1}{w_i}> B
	$$
	\item Since the first $k+1$ items has the highest ratio of profit to weight and its weight sum is greater than $B$, then
	$$
	\sum_{i=1}^{k+1}{p_i}> OPT
	$$
	\item Then we have
	$$
	m_{combined}=max\{m_{ratio},m_{profit}\}\geq \frac{m_{ratio}+m_{profit}}{2}
	$$
	$$
	=\frac{\sum_{i=1}^{k}{p_i}+m_{profit}}{2}\geq \frac{\sum_{i=1}^{k}{p_i}+p_{k+1}}{2}>\frac{OPT}{2}
	$$

\end{itemize}
\newpage




\begin{exercise}
	\textbf{(Maximum Cut)} Given an undirected graph $G=(V,E)$, the \textit{cardinality maximum cut problem} asks for a partition of $V$ into sets $S$ and $\bar{S}$ so that the number of edges running between these sets is maximized. Find a factor $2$ approximation algorithm for this problem.
\end{exercise}

\textbf{Solution:}

\begin{algorithm}[htb]
\caption{Greedy-Algorithm for Maximum Cut}
	\begin{algorithmic}[1]
		\State Define $d(S,T)=|\{(u,v)\mid u\in S, v\in T\}|$
		\State $n=|V|$
		\State $S_0\leftarrow \phi, T_0\leftarrow \phi$
		\For{$v_i\in V,i=1,\ldots,n$}
			\State $S_i\leftarrow S_{i-1}$
			\State $T_i\leftarrow T_{i-1}$
			\If{$d(\{v_i\},S_i)>d(\{v_i\},T_i)$}
			\State $T_i\leftarrow T_i\cup \{v_i\}$
			\Else
			\State $S_i\leftarrow S_i\cup \{v_i\}$
			\EndIf
		\EndFor
		\State
		\Return cut $S_n,T_n$
	\end{algorithmic}
\end{algorithm}

\begin{itemize}
	\item We prove Algorithm 2 has approximation factor $2$. Since every time we add a new vertex to $S_i$ or $T_i$, we add
	$$
	max\{d(\{v_i\},S_i), d(\{v_i\},T_i)\}
	$$
	\item number of edges running between $S_n$ and $T_n$. Thus we have
	$$
	2m=2\sum_{i=1}^{n}{max\{d(\{v_i\},S_i), d(\{v_i\},T_i)\}}\geq \sum_{i=1}^{n}{(d(\{v_i\},S_i)+ d(\{v_i\},T_i))}=|E|\geq OPT=m^*
	$$
	$$
	\Rightarrow \frac{m^*}{m}\leq 2
	$$
\end{itemize}
\newpage




\begin{exercise}
	Consider the following problem: Given an undirected graph and compute the number of matchings (not the cardinality of a single matching, but the number of different ways of matching) in the graph. Show that if we have an $\alpha$-approximation algorithm for it for some constant $\alpha$, then we also have a PTAS.
\end{exercise}

\textbf{Solution:}
\begin{itemize}
	\item Based on the $\alpha$-approximation algorithm $f$, we design the following algorithm. We have
	$$
	\frac{1}{\alpha}*OPT(G)\leq f(G)\leq \alpha*OPT(G)
	$$
	\item First, transform $G$ to $G'=kG$, where $G'$ has $k$ graph $G$s with no edges between them. Then run algorithm $f$ on $G'$, we have
	$$
	\frac{1}{\alpha}*OPT(kG)\leq f(kG)\leq \alpha*OPT(kG), \alpha>1
	$$
	$$
	\Rightarrow \frac{1}{\alpha}*OPT(G)^k\leq f(kG)\leq \alpha*OPT(G)^k
	$$
	$$
	\Rightarrow \frac{1}{\sqrt[k]{\alpha}}*OPT(G)\leq \sqrt[k]{f(kG)}\leq \sqrt[k]{\alpha}*OPT(G)
	$$
	\item Let $k\rightarrow +\infty$, then 
	$$
	\frac{1}{\sqrt[k]{\alpha}}\rightarrow 1,\sqrt[k]{\alpha}\rightarrow 1
	$$
	\item and  we get a PTAS algorithm $f_1(G)=\sqrt[k]{f(kG)}$.
\end{itemize}
\newpage




\begin{exercise}
	Let $G$ be a complete undirected graph in which all edge lengths are either $1$ or $2$. Note, that edge lengths satisfy the triangle inequality. Give a factor $4/3$ approximation algorithm for the TSP in this special class of graphs.
	
	Hint: A $2$-matching in a graph $G$ is a subset of edges $M$, such that every vertex is incident to exactly $2$ edges of $M$. A minimum cost $2$-matching can be computed in polynomial time.
\end{exercise}

\textbf{Solution:}
\begin{itemize}
	\item We have the following algorithm: run minimum cost $2$-matching algorithm on $G$ and get minimum cost $2$-matching $M$. Suppose $M$ consists of $n$ cycles. We remove one edge from each cycle and connect them to be one cycle $M'$ and return $M'$. This runs in polynomial time.
	\item First, since the minimum size of each cycle in $M$ is $3$, we have
	$$
	n\leq \lfloor|V|/3\rfloor 
	$$
	\item Then
	$$
	m=C(M')\leq C(M)+n\leq OPT+\lfloor|V|/3\rfloor \leq OPT+OPT/3=\frac{4}{3}*OPT
	$$
\end{itemize}
\newpage




\end{document}
